Project

### 2022-03-28 Project/DraftR.Rmd
Update DraftR.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PCA

>>>>

GitHub Link:

#Load Package
```{r}
library(dplyr)
library(tidyr)
library(MASS)
library(MuMIn)
library(ggplot2)
library(reshape2)
library(grid)
library(gridExtra)
library(ggfortify)
```

# Import Data
```{r}
###NK & HB lifetime reproductive success data
ltrsHB <- read.csv("./Data/HargreavesEcolLett data ltrsHB.csv")
ltrsNK <- read.csv("./Data/HargreavesEcolLett data ltrsNK.csv")

###NK & HB phenology data
phenNK <- read.csv("./Data/HargreavesEcolLett data phenologyNK.csv")
phenHB <- read.csv("./Data/HargreavesEcolLett data phenologyNK.csv")
```

```{r}
str(phenHB)
```

## PCA
```{r}
# delete rows with NA value
USBwithF1NA <- USBwithF1 %>%
    na.omit
names(USBwithF1NA)
```

Do plants transplanted from low-, mid-, and high- ranges vary in their ability to phenologically adapt to ranges outside their native range? (Fig. 2)
```{r}

```
